Open-source landscape for 3D CSEM modelling

### 2020-07-06 manuscript/Manuscript.tex

The electromagnetics implementations use a staggered grid finite volume
approach where physical properties are discretized at cell centers, fields on
cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
discretizing Maxwell's equations, we recommend \cite{Haber2014b}). There are
two different discretization strategies implemented for Maxwell's equations: (
a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
cell edges and the magnetic flux density ($\vec{h}$) on cell faces, and (b)
the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
edges and the current density ($\vec{j}$) on cell faces. In both cases the
physical properties: electrical conductivity / resistivity and magnetic
permeability are discretized at cell centers. Having multiple implementations
allows for testing that compares results from each approach, as well as the
representation of both electrical and magnetic sources on cylindrically
symmetric meshes. \simpeg supports variable magnetic permeability and
full-tensor anisotropy for the physical properties.

@@

>>>>

The electromagnetics implementations use a staggered grid finite volume
approach where physical properties are discretized at cell centers, fields on
cell edges and fluxes on cell faces \citep{IEEE.66.Yee} (for an overview of
discretizing Maxwell's equations, we recommend \cite{Haber2014b}). There are
two different discretization strategies implemented for Maxwell's equations: (
a) the EB-formulation, which discretizes the electric field ($\vec{e}$) on
cell edges and the magnetic flux density ($\vec{b}$) on cell faces, and (b)
the HJ-formulation, which discretizes the magnetic field ($\vec{h}$) on cell
edges and the current density ($\vec{j}$) on cell faces. In both cases the
physical properties: electrical conductivity / resistivity and magnetic
permeability are discretized at cell centers. Having multiple implementations
allows for testing that compares results from each approach, as well as the
representation of both electrical and magnetic sources on cylindrically
symmetric meshes. \simpeg supports variable magnetic permeability and
full-tensor anisotropy for the physical properties.

@@

\imycom[LH]{From the discussion in slack - also a TODO on adding points on if there were any changes (or new motivation for development) based on this exercise --> goal: highlight benefits of open source collaborations.

Within SimPEG: This work has motivated feature development including: (a)
interpolation and averaging strategies from mapping physical properties on a
fine mesh to a coarser mesh for computation and (b) new examples to include in
the documentation for designing OcTree meshes. Furthermore, as a part of
a broader development objective of interoperating with other
forward-simulation engines, connecting \emg3d and \simpeg provided a
motivating use-case for the latest refactor and release of \simpeg 0.14.0
\citep{simpeg0.14.0}. }
